---
title: "Olympic Basketball"
author: "Sanskar Bachani"
date: "2026-09-30"
format: html
---

How did player ages differ across men's basketball teams at the 2016 Olympics? I used [TidyTuesday data from August 6, 2024](https://github.com/rfordatascience/tidytuesday/blob/main/data/2024/2024-08-06/readme.md) to compare the teams.

The full data cover the Olympics from 1896 to 2016. RGriffin put the Sports Reference records on Kaggle. I kept the men's basketball event in 2016. This gives 141 players from 12 teams. Each player has one row and an age.

```{r}
library(tidyverse)

olympics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-08-06/olympics.csv')

basketball <- filter(olympics, sport == "Basketball", year == 2016, sex == "M")
```

Each box shows the middle half of a team's ages. The line in the box marks the median.

```{r}
ggplot(basketball, aes(x = age, y = team)) +
  geom_boxplot(fill = "darkorange") +
  labs(
    title = "Player ages by team",
    x = "Age (years)",
    y = "Team"
  )
```

China has the lowest median age at 22.5 years. Brazil has the highest at 31. The United States falls between them at 26. Argentina has a wide age range, from 21 to 39.

The records list 10 players for Croatia and 11 for Nigeria. Each other team has 12. These comparisons use the players in the data.

## Sources

- [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/main/data/2024/2024-08-06/readme.md)
- [CSV data](https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-08-06/olympics.csv)
- [Original data on Kaggle](https://www.kaggle.com/datasets/heesoo37/120-years-of-olympic-history-athletes-and-results)
- [Sports Reference](https://www.sports-reference.com/olympics/)
